---
title: "R Notebook"
output: html_notebook
---
#Description
##distribution, mean, and q1,q3
```{r}
# df <- readRDS("imdb.rds")
movie_df <- df %>% 
  filter(titleType == "movie") %>% 
  filter(numVotes >= 10) %>% #numVote >= 10
  group_by(tconst) %>% 
  slice(1) %>% 
  filter(numVotes >= 10) %>%  
  ungroup()

movie_df %>% 
  summarise(rating_q1 = quantile(averageRating, 0.25),
            rating_q3 = quantile(averageRating, 0.75))
```

```{r}
mean <- mean(movie_df$averageRating, na.rm = T) %>% round(2)
movie_df %>% 
  ggplot()+
    geom_histogram(aes(averageRating))+
    geom_vline(xintercept = mean, colour = "red", linetype="dashed", show.legend = T)+
    annotate("text", label = mean, x = mean, y= -1, size = 4, colour = "red")+
    theme_light()
```
#Who is most likeky to be in a bad/good movie?
##Bad movies
```{r}
bad_movie <- movie_df %>% 
  filter(averageRating < 5.4)

bad_movie <- df %>% 
  filter(tconst %in% bad_movie$tconst) 
```
```{r}
bad_movie %>%
  count(nconst, category, primaryName) %>%
  filter(!is.na(primaryName)) %>% 
  arrange(desc(n)) %>% 
  slice(1:50)
```

```{r}
bad_movie %>%
  count(nconst, category, primaryName) %>%
  filter(n >= 20) %>% 
  filter(!is.na(primaryName)) %>% 
  ggplot()+
  geom_col(aes(x = reorder( primaryName, -n), y = n, fill = category))+
  theme(axis.text.x=element_text(angle=45, hjust=1))+
  xlab("Name")
```
##Good movies
```{r}
good_movie <- movie_df %>% 
  filter(averageRating > 7.2)

good_movie <- df %>% 
  filter(tconst %in% good_movie$tconst) 
```
```{r}
good_movie %>%
  count(nconst, category, primaryName) %>%
  filter(!is.na(primaryName)) %>% 
  arrange(desc(n)) %>% 
  slice(1:50)
```
```{r}
good_movie %>%
  count(nconst, category, primaryName) %>%
  filter(!is.na(primaryName)) %>% 
  filter(n >= 10) %>% 
  ggplot()+
  geom_col(aes(x = reorder(primaryName, -n), y = n, fill = category))+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  xlab("Name")
```
# Another view: mean rating of a person
##filtering people at least appear 3 times in different movie and caculate mean rating
```{r}
crew <- df %>% 
  filter(titleType == "movie") %>%  
  filter(numVotes >= 10) %>% 
  count(nconst, tconst) %>% 
  count(nconst) %>% 
  filter(n >= 3) 

crew_average_rating <- df %>% 
  filter(titleType == "movie") %>% 
  filter(numVotes >= 10) %>% 
  filter(nconst %in% crew$nconst) %>% 
  group_by(nconst) %>% 
  mutate(crew_average_rating = mean(averageRating))
```
##Top 10
```{r}
crew_average_rating %>% 
  slice(1) %>% 
  filter(!is.na(primaryName)) %>% 
  ungroup() %>% 
  arrange(desc(crew_average_rating)) %>% 
  top_n(10) %>% 
  ggplot(aes(x = reorder(primaryName, -crew_average_rating), y = crew_average_rating, fill = category)) +
  geom_col() +
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  geom_text(aes(label = crew_average_rating %>% round(2)), vjust = -0.5, size = 3)+
  xlab("Name")
```
## Last 10
```{r}
crew_average_rating %>% 
  slice(1) %>% 
  filter(!is.na(primaryName)) %>% 
  ungroup() %>% 
  arrange(crew_average_rating) %>%  
  top_n(-10) %>% 
  ggplot(aes(x = reorder(primaryName, crew_average_rating), y = crew_average_rating, fill = category))+
  geom_col()+
  theme(axis.text.x=element_text(angle=60, hjust=1))+
  geom_text(aes(label = crew_average_rating %>% round(2)), vjust = -0.5, size = 3)+
  xlab("Name")
```
# who's the highest/lowest rated double?
##Finding doubles appears >= 3 times
```{r}
network_df <- df %>%
  filter(titleType == "movie") %>% 
  filter(numVotes >= 10) %>% 
  select(tconst, nconst, averageRating) %>% 
  group_by(tconst) %>% 
  arrange(desc(nconst)) %>% 
  mutate(next_nconst = lag(nconst)) %>% 
  filter(!is.na(next_nconst)) %>% 
  ungroup() %>% 
  select(-tconst) %>%  
  mutate(id1 = as.numeric(substr(nconst, 3, length(nconst))),
         id2 = as.numeric(substr(next_nconst, 3, length(next_nconst)))) %>% 
  mutate(new_nconst = ifelse(id1 > id2, next_nconst, nconst),
         new_next_nconst = ifelse(id1 > id2, nconst, next_nconst)) %>% 
  mutate(nconst = new_nconst, next_nconst = new_next_nconst) %>%
  select(nconst, next_nconst, averageRating) 

edges <- network_df %>%
  count(nconst, next_nconst) %>% 
  filter(n>=3)

double_rating <- network_df %>%
  right_join(edges, by = c("nconst", "next_nconst")) %>% 
  filter(!is.na(n)) %>% 
  group_by(nconst, next_nconst) %>% 
  mutate(double_average_rating = mean(averageRating)) %>% 
  select(-averageRating)
```
###Define a person's main category
```{r}
crew_main_cat <- df %>% 
  group_by(nconst) %>% 
  count(category) %>% 
  arrange(desc(n)) %>% 
  slice(1) %>% 
  select(-n)

crew_name <- df %>% 
  select(nconst, primaryName) %>% 
  group_by(nconst, primaryName) %>% 
  slice(1) %>% 
  ungroup()
```
###Merge tables
```{r}
double_rating <- double_rating %>%
  left_join(crew_main_cat, by = "nconst") %>% 
  rename(nconst_cat = category) %>% 
  left_join(crew_main_cat, by = c("next_nconst" = "nconst")) %>% 
  rename(next_nconst_cat = category)

double_rating <- double_rating %>% 
  left_join(crew_name, by = "nconst") %>% 
  rename(nconst_name = primaryName) %>% 
  left_join(crew_name, by = c("next_nconst" = "nconst")) %>% 
  rename(next_nconst_name = primaryName)
```
###Top 10
```{r}
double_rating %>% 
  ungroup() %>% 
  arrange(desc(double_average_rating)) %>% 
  slice(1:10)
```
### Last 10
```{r}
double_rating %>% 
  ungroup() %>% 
  arrange(double_average_rating) %>% 
  slice(1:10)
```

#Clustering for crews
```{r}
library(igraph)
g <- graph_from_data_frame(double_rating %>% select(nconst, next_nconst, n, double_average_rating),
                           directed = F,
                           )
ecount(g)
```
##Community analysis
```{r}
community <- cluster_leading_eigen(g, weights=E(g)$n)
community
```
###Defining nodes attributes
```{r}
V(g)$community <- community$membership
nodes_df <- igraph::as_data_frame(g, what = "vertices") %>% 
  left_join(crew_average_rating %>%
              slice(1) %>% 
              select(nconst, crew_average_rating, primaryName), by = c("name" = "nconst")) %>% 
  left_join(crew_main_cat, by = c("name" = "nconst"))
```
###Find best/worst communitis with 5 or more members
```{r}
community_over_5 <- nodes_df %>%
  count(community) %>% 
  arrange(desc(n)) %>% 
  filter(n >= 5)

community_over_5
```
```{r}
community_rating <- nodes_df %>% 
  filter(community %in% community_over_5$community) %>% 
  group_by(community) %>% 
  mutate(community_average_rating = mean(crew_average_rating)) %>% 
  slice(1) %>% 
  select(community, community_average_rating)

community_rating %>% arrange(desc(community_average_rating))
```
####Who is in the best/worst community?
Best community
```{r}
nodes_df %>% filter(community == 672)
```
Worst Community
```{r}
nodes_df %>% filter(community == 333)
```
###Visualization of community over 5 members
```{r}
library(visNetwork)

g <- graph_from_data_frame(double_rating %>% select(nconst, next_nconst, n, double_average_rating),
                           directed = F,
                           vertices = nodes_df)

sub_g <- induced_subgraph(g, which(V(g)$community %in% community_over_5$community))

sub_g_vis <- toVisNetworkData(sub_g)
sub_g_vis$nodes <- sub_g_vis$nodes %>%
  rename(group = category, id = label, label = primaryName) 

visNetwork(nodes = sub_g_vis$nodes, edges = sub_g_vis$edges) %>% 
    visInteraction(navigationButtons = TRUE) %>% 
    visOptions(highlightNearest = TRUE, selectedBy  = "community") 
```



##Other clustring mothods
Results looks bad.
###Making adjacency & similarity matrix
```{r}
A <- as_adjacency_matrix(g, attr = "n")
S <- qlcMatrix::corSparse(A)

```
### Hierachical clustering
```{r}
H <- 1-S
d <- as.dist(H)
```

```{r}
factoextra::fviz_nbclust(S, 
             FUNcluster = factoextra::hcut,
             method = "silhouette",     
             k.max = 20          
             ) + 
  labs(title="Silhouette method") 
# 2 cluster is the best
```

```{r}
hc_cluster_tree <- hclust(d, method = "average")
hc_cluster <- cutree(hc_cluster_tree, k=2)
V(g)$hc_cluster <- hc_cluster

df_cluster %>% 
  group_by(hc_cluster) %>% 
  summarise(n = n(),
            mean_rating = mean(crew_average_rating))
```

###Spectral clustring
```{r}
# http://www.di.fc.ul.pt/~jpn/r/spectralclustering/spectralclustering.html
make_affinity <- function(S, n.neighboors=2) {
  N <- length(S[,1])

  if (n.neighboors >= N) {  # fully connected
    A <- S
  } else {
    A <- matrix(rep(0,N^2), ncol=N)
    for(i in 1:N) { # for each line
      # only connect to those points with larger similarity 
      best.similarities <- sort(S[i,], decreasing=TRUE)[1:n.neighboors]
      for (s in best.similarities) {
        j <- which(S[i,] == s)
        A[i,j] <- S[i,j]
        A[j,i] <- S[i,j] # to make an undirected graph, ie, the matrix becomes symmetric
      }
    }
  }
  A  
}
```

```{r}
A <- make_affinity(S, 3)
D <- diag(apply(A, 1, sum))
U <- D - A
```

```{r}
"%^%" <- function(M, power){
  with(eigen(M), vectors %*% (values^power * solve(vectors)))
}
  
k <- 2
evL <- eigen(U, symmetric=TRUE)
Z <- evL$vectors[,(ncol(evL$vectors)-k+1):ncol(evL$vectors)]
```
```{r}
plot(1:10, rev(evL$values)[1:10])
```
```{r}
sp_cluster <- kmeans(Z, centers=2)
V(g)$sp_cluster <- sp_cluster$cluster
```

```{r}
df_cluster <- igraph::as_data_frame(g, what = "vertices") %>% 
  left_join(crew_average_rating %>% slice(1) %>% select(nconst, crew_average_rating),
            by = c("name" = "nconst"))
```
```{r}
df_cluster %>% 
  group_by(sp_cluster) %>% 
  summarise(n = n(),
            mean_rating = mean(crew_average_rating))
```

```{r}
df_cluster %>% 
  mutate(sp_cluster = as.factor(sp_cluster)) %>% 
  group_by(sp_cluster) %>% 
  mutate(mean = mean(crew_average_rating)) %>% 
  ggplot +
  geom_density(aes(crew_average_rating, color = sp_cluster))+
  geom_vline(aes(xintercept = mean, color=sp_cluster),
               linetype="dashed")+
  xlab("mean rating") +
  theme_minimal()
```






#Clustering for movies
```{r}
const <- df %>% 
  filter(titleType == "movie") %>%  
  filter(numVotes >= 100) %>% 
  group_by(nconst, tconst) %>%
  slice(1) %>% #Each person can only appears one time in each movie
  select(tconst, nconst) %>% 
  ungroup()
```

```{r}
library(Matrix)
toAdjMatrix <- function(df){
	A <- spMatrix(nrow=length(unique(df$nconst)),
				  ncol=length(unique(df$tconst)),
				  i = as.numeric(factor(df$nconst)),
				  j = as.numeric(factor(df$tconst)),
				  x = rep(1, length(as.numeric(df$nconst))) )
	row.names(A) <- levels(factor(df$nconst))
	colnames(A) <- levels(factor(df$tconst))
	Acol <- tcrossprod(t(A))
	Matrix(Acol)
}

A <- toAdjMatrix(const)
A <- A / apply(A, 1, max)

A[1:10, 1:10]
```
```{r}
factoextra::fviz_nbclust(as.matrix(A), 
             FUNcluster = kmeans,
             method = "silhouette",     
             k.max = 16          
             ) + 
  labs(title="Silhouette method") 
```
